Article Title

### 2021-03-02 Paper.tex
update Arabidopsis GOA and finalize quality and quantity tables

\caption{\label{tab:cleanup-table}Number of removed annotations during cleanup.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{llrrr}
\toprule
Genome & Dataset & Obsolete Annotations & Duplicates & Annotations with Modifiers\\
\midrule
\rowcolor{gray!6}  \textit{Arachis hypogaea} & GOMAP & 0 & 0 & 912\\
\cmidrule{1-5}
\textit{Brachypodium distachyon} & GOMAP & 696 & 43 & 789\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 203 & 0 & 930\\
\cmidrule{1-5}
\textit{Gossypium raimondii} & GOMAP & 184 & 0 & 822\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 101 & 0 & 815\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & GoldStandard & 0 & 4 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & GOMAP & 0 & 0 & 798\\
\cmidrule{1-5}
\textit{Medicago truncatula} R108 & GOMAP & 0 & 0 & 803\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 111 & 2 & 869\\

 & GoldStandard & 38 & 556 & 0\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14 & 0\\
\cmidrule{1-5}
\textit{Phaseolus vulgaris} & GOMAP & 0 & 0 & 783\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Sorghum bicolor} & GOMAP & 690 & 59 & 783\\
\cmidrule{1-5}
 & GOMAP & 285 & 0 & 1132\\

\rowcolor{gray!6}   & GoldStandard & 0 & 10 & 0\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Vigna unguiculata} & GOMAP & 0 & 0 & 811\\
\cmidrule{1-5}
 & GOMAP & 1106 & 70 & 709\\

\rowcolor{gray!6}   & GoldStandard & 1 & 11 & NA\\

 & Gramene49 & 94 & 2 & 0\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0 & 0\\
\cmidrule{1-5}
 & GOMAP & 752 & 83 & 848\\

\rowcolor{gray!6}   & GoldStandard & 55 & 174 & 0\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 726 & 77 & 823\\
\cmidrule{1-5}
\textit{Zea mays} PH207 & GOMAP & 798 & 76 & 830\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 754 & 82 & 840\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/cleanup/results/cleanup_table.csv}{Download this table (CSV)}
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets. CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Genes Annotated[\%]\textsuperscript{a}} & \multicolumn{4}{c}{Annotations\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & CC & BF & MP & A & CC & BF & MP & A & CC & BF & MP & A\\
\midrule
\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.90 & 84.69 & 100.00 & 100.00 & 153,052 & 132,624 & 493,588 & 779,264 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\textit{Brachypodium distachyon} & 34,310 & GOMAP & 81.37 & 85.36 & 100.00 & 100.00 & 75,536 & 69,452 & 255,616 & 400,604 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.02 & 88.93 & 100.00 & 100.00 & 128,836 & 113,491 & 417,340 & 659,667 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.06 & 92.37 & 100.00 & 100.00 & 96,442 & 85,234 & 307,727 & 489,403 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 88.67 & 91.77 & 100.00 & 100.00 & 87,780 & 80,015 & 272,625 & 440,420 & 2 & 2 & 5 & 10\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & \multirow{-2}{*}{\raggedleft\arraybackslash 39,734} & GoldStandard & 0.02 & 0.05 & 0.05 & 0.07 & 7 & 23 & 45 & 75 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.69 & 100.00 & 100.00 & 107,019 & 99,452 & 363,877 & 570,348 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.39 & 90.14 & 100.00 & 100.00 & 111,991 & 107,769 & 382,133 & 601,893 & 1 & 2 & 5 & 9\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 79.87 & 83.31 & 100.00 & 100.00 & 72,415 & 64,386 & 248,495 & 385,296 & 2 & 2 & 6 & 9\\

 &  & GoldStandard & 15.98 & 20.61 & 25.21 & 31.79 & 7,730 & 11,060 & 19,378 & 38,176 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-3}{*}{\raggedleft\arraybackslash 35,825} & Gramene61-IEA & 30.07 & 43.37 & 46.63 & 59.86 & 14,633 & 32,787 & 39,105 & 86,529 & 1 & 1 & 1 & 3\\
\cmidrule{1-15}
\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.52 & 93.07 & 100.00 & 100.00 & 71,658 & 64,328 & 229,449 & 365,435 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Sorghum bicolor} & 34,129 & GOMAP & 82.48 & 85.98 & 100.00 & 100.00 & 76,343 & 69,937 & 259,229 & 405,509 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
 &  & GOMAP & 88.60 & 90.98 & 100.00 & 100.00 & 267,317 & 218,186 & 785,689 & 1,271,192 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 0.89 & 0.57 & 1.54 & 1.73 & 1,590 & 923 & 4,807 & 7,323 & 1 & 0 & 2 & 3\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene61-IEA & 26.74 & 55.24 & 48.72 & 70.24 & 38,975 & 109,319 & 109,518 & 257,832 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.26 & 91.08 & 100.00 & 100.00 & 75,513 & 68,040 & 243,094 & 386,647 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
 &  & GOMAP & 88.33 & 96.42 & 99.99 & 100.00 & 134,917 & 87,166 & 291,091 & 513,174 & 3 & 2 & 6 & 11\\

\rowcolor{gray!6}   &  & GoldStandard & 3.89 & 0.15 & 0.38 & 4.10 & 1,554 & 65 & 299 & 1,918 & 1 & 0 & 0 & 1\\

 &  & Gramene49 & 29.98 & 45.58 & 40.03 & 55.55 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & \multirow{-4}{*}{\raggedleft\arraybackslash 39,469} & Phytozome & 11.46 & 34.78 & 28.79 & 40.87 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
 &  & GOMAP & 93.36 & 94.93 & 100.00 & 100.00 & 88,468 & 81,963 & 278,518 & 448,949 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 21.23 & 25.60 & 30.82 & 38.07 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene61-IEA & 37.57 & 56.11 & 60.94 & 74.13 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Zea mays} Mo17 & 38,620 & GOMAP & 87.04 & 90.88 & 100.00 & 100.00 & 87,221 & 78,938 & 277,586 & 443,745 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\textit{Zea mays} PH207 & 40,557 & GOMAP & 86.71 & 90.62 & 100.00 & 100.00 & 90,267 & 85,223 & 288,474 & 463,964 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Zea mays} W22 & 40,690 & GOMAP & 90.89 & 92.59 & 100.00 & 100.00 & 95,043 & 84,750 & 289,576 & 469,369 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}
\item[a] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them? A = How many at least one from any aspect? ($\textrm{A} = \textrm{CC} \cup \textrm{BF} \cup \textrm{MP}$)
\item[b] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Please note that $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{llrr>{}r|rrr}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{3}{c}{SimGIC2} & \multicolumn{3}{c}{TC-AUCPCR} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
Genome & Dataset & CC & BF & MP & CC & BF & MP\\
\midrule
\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.309334 & 0.424286 & 0.180110 & NaN & 0.000493 & 0.000388\\
\cmidrule{1-8}
 & GOMAP & 0.499374 & 0.448762 & 0.213827 & 0.274482 & 0.261767 & 0.142014\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.416283 & 0.415342 & 0.324981 & 0.170662 & 0.257685 & 0.126104\\
\cmidrule{1-8}
 & GOMAP & 0.474972 & 0.418110 & 0.202528 & 0.014568 & 0.005485 & 0.009287\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.384973 & 0.346840 & 0.191962 & 0.004446 & 0.006115 & 0.004811\\
\cmidrule{1-8}
 & GOMAP & 0.235407 & 0.348389 & 0.096186 & 0.035907 & 0.001639 & 0.001017\\

\rowcolor{gray!6}   & Gramene49 & 0.299075 & 0.359259 & 0.164630 & 0.055498 & 0.003230 & 0.001965\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.186238 & 0.347164 & 0.100965 & 0.014873 & 0.003058 & 0.000540\\
\cmidrule{1-8}
\rowcolor{gray!6}   & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{\label{tab:cleanup-table}Number of removed annotations during cleanup.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{llrrr}
\toprule
Genome & Dataset & Obsolete Annotations & Duplicates & Annotations with Modifiers\\
\midrule
\rowcolor{gray!6}  \textit{Arachis hypogaea} & GOMAP & 3437 & 13 & 912\\
\cmidrule{1-5}
 & GOMAP & 2512 & 49 & 789\\

\rowcolor{gray!6}   & GoldStandard & 21 & 204 & 0\\

 & Gramene63-IEA & 166 & 114 & 0\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & Phytozome12 & 99 & 18 & 0\\
\cmidrule{1-5}
\textit{Cannabis sativa} & GOMAP & 1714 & 6 & 757\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 3333 & 10 & 930\\
\cmidrule{1-5}
\textit{Gossypium raimondii} & GOMAP & 1781 & 7 & 822\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 1877 & 8 & 815\\

 & GoldStandard & 1 & 9 & 0\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & Gramene63-IEA & 282 & 147 & 0\\
\cmidrule{1-5}
 & GOMAP & 2673 & 10 & 798\\

\rowcolor{gray!6}   & GoldStandard & 2 & 23 & 0\\

 & Gramene62-IEA & 429 & 251 & 0\\

\rowcolor{gray!6}   & Gramene63-IEA & 309 & 243 & 0\\

\multirow{-5}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & Phytozome12 & 132 & 17 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & GOMAP & 4168 & 7 & 803\\
\cmidrule{1-5}
 & GOMAP & 1642 & 7 & 869\\

\rowcolor{gray!6}   & GoldStandard & 37 & 833 & 0\\

 & Gramene61-IEA & 242 & 28 & 0\\

\rowcolor{gray!6}   & Gramene63-IEA & 238 & 64 & 0\\

\multirow{-5}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Phytozome12 & 119 & 19 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 1190 & 6 & 783\\
\cmidrule{1-5}
\textit{Pinus lambertiana} & GOMAP & 1839 & 4 & 587\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 2384 & 66 & 783\\

 & GoldStandard & 178 & 219 & 0\\

\rowcolor{gray!6}   & Gramene63-IEA & 278 & 198 & 0\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & Phytozome12 & 131 & 12 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 9624 & 17 & 1132\\

 & GoldStandard & 1 & 5 & 0\\

\rowcolor{gray!6}   & Gramene61-IEA & 706 & 88 & 0\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene63-IEA & 584 & 319 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 1269 & 6 & 811\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Vigna unguiculata}} & Phytozome12 & 122 & 27 & 0\\
\cmidrule{1-5}
\rowcolor{gray!6}   & GOMAP & 2077 & 89 & 848\\

 & GoldStandard & 50 & 633 & 0\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene63-IEA & 306 & 140 & 0\\
\cmidrule{1-5}
 & GOMAP & 2346 & 83 & 823\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} Mo17} & GoldStandard & 36 & 1489 & 0\\
\cmidrule{1-5}
 & GOMAP & 2676 & 82 & 830\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} PH207} & GoldStandard & 37 & 2702 & 0\\
\cmidrule{1-5}
 & GOMAP & 2681 & 88 & 840\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} W22} & GoldStandard & 30 & 499 & 0\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/cleanup/results/cleanup_table.csv}{Download this table (CSV)}
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets. CC, MF, BP, and A refer to the aspects of the GO: Cellular Component, Molecular Function, Biological Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Genes Annotated[\%]\textsuperscript{a}} & \multicolumn{4}{c}{Annotations\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & CC & MF & BP & A & CC & MF & BP & A & CC & MF & BP & A\\
\midrule
\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.85 & 84.68 & 100.00 & 100.00 & 150,525 & 132,144 & 493,145 & 775,814 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
 &  & GOMAP & 81.33 & 85.35 & 100.00 & 100.00 & 74,172 & 69,213 & 255,397 & 398,782 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 21.54 & 19.53 & 18.20 & 26.66 & 10,985 & 10,436 & 11,120 & 32,673 & 1 & 1 & 1 & 3\\

 &  & Gramene63-IEA & 33.12 & 49.29 & 38.29 & 63.60 & 21,658 & 36,372 & 23,899 & 82,026 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & \multirow{-4}{*}{\raggedleft\arraybackslash 34,310} & Phytozome12 & 10.25 & 37.21 & 26.86 & 43.11 & 4,186 & 18,597 & 11,070 & 34,060 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\textit{Cannabis sativa} & 33,677 & GOMAP & 94.22 & 95.48 & 100.00 & 100.00 & 85,755 & 73,614 & 262,741 & 422,110 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 86.95 & 88.92 & 100.00 & 100.00 & 126,470 & 113,068 & 416,989 & 656,527 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.00 & 92.37 & 100.00 & 100.00 & 95,419 & 84,910 & 307,470 & 487,799 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 88.57 & 91.76 & 100.00 & 100.00 & 86,489 & 79,727 & 272,420 & 438,636 & 2 & 2 & 5 & 10\\

 &  & GoldStandard & 28.23 & 26.30 & 23.43 & 35.64 & 15,734 & 15,391 & 15,267 & 46,414 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,734} & Gramene63-IEA & 36.19 & 50.90 & 41.71 & 65.03 & 29,826 & 44,789 & 29,425 & 104,178 & 1 & 1 & 1 & 3\\
\cmidrule{1-15}
 &  & GOMAP & 83.79 & 86.69 & 100.00 & 100.00 & 104,902 & 99,155 & 363,608 & 567,665 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 25.45 & 23.26 & 21.51 & 32.12 & 17,938 & 18,416 & 18,461 & 54,827 & 1 & 1 & 1 & 3\\

 &  & Gramene63-IEA & 34.25 & 50.84 & 40.26 & 66.14 & 32,753 & 63,470 & 40,441 & 137,001 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & \multirow{-4}{*}{\raggedleft\arraybackslash 50,444} & Phytozome12 & 8.87 & 36.05 & 25.83 & 41.07 & 5,315 & 25,950 & 15,576 & 47,098 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.10 & 90.14 & 100.00 & 100.00 & 108,388 & 107,499 & 381,831 & 597,718 & 1 & 2 & 5 & 9\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 79.78 & 83.31 & 100.00 & 100.00 & 71,306 & 64,150 & 248,304 & 383,760 & 2 & 2 & 6 & 9\\

 &  & GoldStandard & 29.95 & 27.29 & 25.33 & 37.57 & 15,492 & 15,176 & 16,536 & 47,339 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}   &  & Gramene63-IEA & 32.21 & 45.83 & 36.75 & 60.13 & 21,935 & 37,425 & 24,255 & 83,645 & 1 & 1 & 1 & 3\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-4}{*}{\raggedleft\arraybackslash 35,825} & Phytozome12 & 10.31 & 40.10 & 29.18 & 46.09 & 4,361 & 20,842 & 12,451 & 37,884 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.48 & 93.06 & 100.00 & 100.00 & 70,987 & 64,022 & 229,230 & 364,239 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\textit{Pinus lambertiana} & 31,007 & GOMAP & 92.67 & 95.91 & 100.00 & 100.00 & 71,247 & 68,315 & 212,248 & 351,810 & 2 & 2 & 5 & 10\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 82.44 & 85.98 & 100.00 & 100.00 & 75,145 & 69,659 & 259,004 & 403,808 & 2 & 2 & 6 & 10\\

 &  & GoldStandard & 34.48 & 32.91 & 30.90 & 42.84 & 16,837 & 17,614 & 17,850 & 52,593 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}   &  & Gramene63-IEA & 35.91 & 52.11 & 42.36 & 67.41 & 23,608 & 39,418 & 27,074 & 90,313 & 1 & 1 & 1 & 3\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & \multirow{-4}{*}{\raggedleft\arraybackslash 34,129} & Phytozome12 & 10.54 & 39.19 & 27.90 & 45.10 & 4,246 & 19,724 & 11,432 & 35,599 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 88.53 & 90.98 & 100.00 & 100.00 & 259,318 & 217,467 & 785,051 & 1,261,836 & 2 & 2 & 6 & 10\\

 &  & GoldStandard & 2.98 & 2.78 & 2.56 & 3.82 & 4,727 & 4,512 & 4,793 & 14,035 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene63-IEA & 29.12 & 58.62 & 38.72 & 70.41 & 47,595 & 111,889 & 62,977 & 222,721 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
 &  & GOMAP & 91.21 & 91.08 & 100.00 & 100.00 & 74,791 & 67,734 & 242,847 & 385,372 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Vigna unguiculata}} & \multirow{-2}{*}{\raggedleft\arraybackslash 29,773} & Phytozome12 & 13.91 & 45.68 & 34.14 & 53.06 & 5,107 & 19,962 & 12,209 & 37,534 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
 &  & GOMAP & 93.16 & 94.92 & 100.00 & 100.00 & 87,648 & 81,665 & 278,305 & 447,618 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 37.92 & 34.78 & 32.67 & 46.85 & 22,531 & 21,292 & 23,153 & 67,285 & 1 & 1 & 1 & 3\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene63-IEA & 39.16 & 58.16 & 48.21 & 73.87 & 30,189 & 53,748 & 35,276 & 119,273 & 1 & 1 & 1 & 3\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 86.98 & 90.87 & 100.00 & 100.00 & 86,074 & 78,650 & 277,395 & 442,119 & 2 & 2 & 6 & 10\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} Mo17} & \multirow{-2}{*}{\raggedleft\arraybackslash 38,620} & GoldStandard & 27.56 & 25.20 & 23.73 & 33.98 & 16,128 & 15,384 & 16,489 & 48,220 & 1 & 1 & 1 & 3\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 86.55 & 90.61 & 100.00 & 100.00 & 88,962 & 84,910 & 288,208 & 462,080 & 2 & 2 & 6 & 10\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} PH207} & \multirow{-2}{*}{\raggedleft\arraybackslash 40,557} & GoldStandard & 28.18 & 25.82 & 24.26 & 34.66 & 17,370 & 16,580 & 17,791 & 51,984 & 1 & 1 & 1 & 3\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 90.77 & 92.58 & 100.00 & 100.00 & 93,622 & 84,450 & 289,364 & 467,436 & 2 & 2 & 6 & 10\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} W22} & \multirow{-2}{*}{\raggedleft\arraybackslash 40,690} & GoldStandard & 25.40 & 23.15 & 21.80 & 31.29 & 15,518 & 14,818 & 15,850 & 46,402 & 1 & 1 & 1 & 3\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}
\item[a] How many genes in the genome have at least one GO term from the CC, MF, BP aspect annotated to them? A = How many at least one from any aspect? ($\textrm{A} = \textrm{CC} \cup \textrm{MF} \cup \textrm{BP}$)
\item[b] How many annotations in the CC, MF, and BP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{MF} + \textrm{BP}$
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Please note that $\textrm{A} \neq \textrm{CC} + \textrm{MF} +\textrm{BP}$
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{llrr>{}r|rr>{}r|rrr}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{3}{c}{SimGIC2} & \multicolumn{3}{c}{TC-AUCPCR} & \multicolumn{3}{c}{Fmax} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8} \cmidrule(l{3pt}r{3pt}){9-11}
Genome & Dataset & CC & MF & BP & CC & MF & BP & CC & MF & BP\\
\midrule
\rowcolor{gray!6}   & GOMAP & 0.404149 & 0.464127 & 0.223830 & 0.233442 & 0.230701 & 0.118526 & 0.741361 & 0.740897 & 0.526881\\

 & Gramene63-IEA & 0.317801 & 0.420859 & 0.349406 & 0.129163 & 0.192507 & 0.111361 & 0.691016 & 0.738542 & 0.650325\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & Phytozome12 & 0.370264 & 0.370521 & 0.352206 & 0.112582 & 0.136832 & 0.085628 & 0.717759 & 0.697076 & 0.660603\\
\cmidrule{1-11}
 & GOMAP & 0.400087 & 0.470012 & 0.238177 & 0.237231 & 0.261399 & 0.130784 & 0.745272 & 0.750213 & 0.560096\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & Gramene63-IEA & 0.306119 & 0.426601 & 0.381010 & 0.157352 & 0.228797 & 0.136002 & 0.680996 & 0.742638 & 0.665696\\
\cmidrule{1-11}
 & GOMAP & 0.371795 & 0.451258 & 0.213407 & 0.272809 & 0.282650 & 0.139032 & 0.730838 & 0.726991 & 0.531406\\

\rowcolor{gray!6}   & Gramene63-IEA & 0.329600 & 0.437274 & 0.343561 & 0.176497 & 0.265887 & 0.133503 & 0.701093 & 0.749900 & 0.654297\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & Phytozome12 & 0.358311 & 0.367257 & 0.363013 & 0.144247 & 0.170863 & 0.110386 & 0.717307 & 0.698429 & 0.661233\\
\cmidrule{1-11}
\rowcolor{gray!6}   & GOMAP & 0.408945 & 0.482650 & 0.248207 & 0.298502 & 0.303384 & 0.159724 & 0.751121 & 0.757181 & 0.559221\\
